---
title: "Externalization - example 1"
output:
  html_document: default
  github_document: default
---

**Externalization**:  import in child scripts into existing parent code


I think this is **easiest to learn from existing examples.**

- [Parent script](01_example.Rmd)
- [Child script 1](src/example_starwars.R)
- [Child script 2](src/example_trees.Rmd)
- [Output -- GitHub Markdown Document](01_example.md)
- [Output -- GitHub 01_example.html](01_example.html)


**However**, if you dare there is more explanation/documentation is below....

## Citations

See

- Xie. [Child Documents](https://yihui.org/knitr/demo/child/)
- Ross.  [Making use of external R code in knitr and R markdown](http://zevross.com/blog/2014/07/09/making-use-of-external-r-code-in-knitr-and-r-markdown/)
- \@Opyate. [Stack Overflow](https://stackoverflow.com/questions/14796501/is-it-possible-to-call-external-r-script-from-r-markdown-rmd-in-rstudio)

## Steps

1. Have a parent .Rmd script (01_example.Rmd)
1. Have at least one child script (`src/example_starwars.R` | `src/example_trees.Rmd`)
1. In the parent script, use the ``knitr::read_chunk`` function to import code "chunks" from the child script.

    - each child "chunk" (subroutine) is delimited by a chunk name.  That name is used in the parent code chunk
    - e.g. Child.R script contains label sub-routins:  e.g. `## @knitr chunk_name` where `chunk_name` varies according to the sub-routine

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE)
knitr::read_chunk('src/example_starwars.R')
```

## Load Libraries

1. A separate chunk, in the Parent, can now call a sub-routine within the child script simply by using the child chunk "name" as the parent code chunk name. 

    - Again, the child chunk name is in the child script, a label following the `@knitr` disgnation, following a `#` comment tag in the first postion of the line.
    
        - e.g. `# @knitr load_libraries`
    
    - Meanwhile, the parent code-chunk name is the name of the child code-chunk name
    
        - e.g. `{r load_libraries}`
        - of course, this is a standard code chund so the above is preceeded by three back ticks, and a following, closing, line of three back ticks.  Just the way any R Markdown code-chunk appears.


```{r load_libraries}
```


## Load Data

```{r load_data}
```


## Display Data

```{r display_data}
```

## Viz

```{r visualize_data}
```

## Tree Plot

Now there is this one problem that an R Markdown document can only use a code-chunk name once in a document.  But you can easily get around this problem by using different parent code-chunk names, along with the `child` argument in the code-chunk code header

    - e.g.
    
        - `{r trees1,  child='src/example_trees.Rmd'}`
        - `{r trees2,  child='src/example_trees.Rmd'}`
        
These two examples actually do the same thing.  But since there are different code chunk names, they child code can be reused within the parent document.  The catch that I see here is that the child-chunk now has to be a .Rmd file and can only have a single sub-routine (code-chunk) within it.

Let's use some base R:  plot the on-board `trees` dataset

Trees example one

```{r child='src/example_trees.Rmd'}
```

Trees example two

```{r child='src/example_trees.Rmd'}
```


## Summary

There are at least two options.  They work interchangeably

Option 1:

- Store multiple sub-routines in a single .R script

     - each sub-routine name is a `#`comment, followed by `@kniter`, followed by the chunk name
     - In the parent file, there must be at least one parent code chunk with the `kinter::read_chunk()` function
     - This child chunk name becomes the chunk name for a code chunk in the parent .Rmd file
     
     
Option 2:

- Store each sub-routine as a separate .Rmd file

    - The child sub-routine must be written inside a standard .Rmd code-chunk
    - The sub-routine is called in the parent .Rmd with the `child=` argument of the parent code-chunk header
    - This sub-routine can be reused within the parent document
     



## Fun Final Example

### Imaginary Thanksgiving Conversation

The next sub-routing is from the master child document example_starwars.R.  The purpose is to create a vector from a tabular dataset of presidential information.

```{r get_repub_prezes}
```

Now I'll use that vector with inline code, below....


TH:  Do you know the names of the Republican presidents?

NP:  No.

TH:  Well you've got:  **r `repub_prezes_vector`**.  That's it.

NP:  There are more.  Right?

TH:  I don't wanna to talk any more.


